Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-01-04 paper.tex
Implement changes elton 20181224

The dielectric constant $\varepsilon$ (also known as the relative
permittivity) plays a crucial role in bridging various fundamental
material properties, such as bandgaps
\cite{Moss_1950_relation,Moss_1985_n_Eg}, optical absorption
\cite{kittel_2005_introduction}, and conductivities
\cite{Dressel_2001_electrodynamics}. $\varepsilon$ characterizes the
ability to screen an electric field $\boldsymbol{E}$ which classifies
metals, semiconductors and insulators.  \todo[inline]{I shortened the
  sentences. However, can we really "classify" the material only by
  $\varepsilon$? For instance HfO2 has large $\varepsilon$ but also
  large bandgap}
% Such definitions determine a broad range of
% condensed matter physics, as well as in related fields in chemistry
% and materials science.
The ability to compute and measure
$\varepsilon$ in bulk materials is well established via different
theoretical and experimental techniques of distinct flavors where the
probe of the dielectric properties is made through an external
electric field.
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or only an 
additional parameter from the bulk-counterparts. 

@@

external electric field. For the majority of 2D nonmetals, the

@@

negligible \todo[inline]{why only nonmetals?  Could you cite one
  reference?}.  Considering that the 2D material is placed in vacuum

@@

components, namely the in-plane

@@

dipoles along the \textit{z}-direction as the charge density
difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$, at zero and
finite electric fields
($|\boldsymbol{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$) extends to
$\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a} and
Supplementary Figure \ref{SI-fig:rho-profile}). When $L$ is large

@@

However, we can see from Eqs. \ref{eq:def-eps-1} that both

@@

the cell $\Omega$.  Therefore, any calculation performed using such

@@

as a function of $L$ for P$\bar{6}$m2 transitional metal

@@

respectively).  Despite of the magnitudes of $L$ both components of
the dielectric constant change systematically without a clear
convergence.

@@

techniques, G$_{\rm 0}$W$_{0}$, and also taking into account
electron-hole excitations at the level of the Bethe-Salpeter equation
(BSE) for the frequency-dependent
$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ invariably give alike
results(details see Supplementary Section \ref{SI-ssec:gw}).

@@

of the respective bulk materials (details see Supplementary Section

@@

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Section \ref{SI-ssec:gw}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability
and comparison with other methods can be found in Supplementary Section \ref{SI-sec:2D-3D-rescale}.

@@

\ref{SI-sec:pol-2D-Eg}). It is worth mentioning that materials with
elements having large polarizabilities, such as Hf and Zr in
1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
for the layers with slightly variations between 1T and 2H phases. The
former normally shows larger values of
$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
\todo[inline]{sorry but I don't quite get the idea of this
  sentence. In fact HfO2 and ZrO2 have quite low in-plane
  polarizabilities compared with even TiO2. Shall we just remove these
  sentenses? }

@@

of theory are needed to predict bandgaps.  We also show that the
proposed Eq. \ref{eq:2D-Moss-para} behaves equivalently well when
using the experimentally accessible optical bandgap of 2D materials (
Supplementary Figure \ref{SI-fig:opt}).

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}{\bf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
This results indicate that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
physical meaning through the geometry of the layer.  Similar to the
molecular polarizability which characterizes the volume of electron
cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section
\ref{SI-ssec:theory-1-perp-fundamental}). Indeed, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
\ref{fig-3}{\bf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ measurable via
electronic and optical approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
is in reality the (dielectric) characteristic thickness of a 2D
material, and can be used to resolve the long-existing controversy
about the experimental thickness of 2D materials, such as graphene
\cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06 level, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
database \cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\bf c} and
\ref{fig-3}{\bf d} (see details in Supplementary Section
\ref{SI-sec:gpaw-1}). Although the dielectric properties may be
overestimated at PBE level due to underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results (see
details in Supplementary Section \ref{SI-sec:gpaw-2}).

@@

We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
%The dielectric constant $\varepsilon$, although not well-defined for
%a monolayer 2D material, becomes applicable when the 2D layers are
%stacked. 
%
%
%
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\bf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis), as show in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

>>>>

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions, e.g. electron-electron. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or it can be used only as an 
additional parameter from the bulk-counterparts.

@@

external electric field. For the majority of the 2D nanosheets, the

@@

negligible.  Considering that the 2D material is placed in vacuum

@@

components of $\kappa$, namely the in-plane

@@

dipoles along the \textit{z}-direction in a range of 
$\sim{}$5--6 \AA{} into the vacuum (Figure \ref{fig-1}{\bf a} and
Supplementary Figure \ref{SI-fig:rho-profile}). 
When $L$ is large

@@

However, we can see from Eq. \ref{eq:def-eps-1} that both

@@

the cell $\Omega$. In the case of bulk materials such physical dependence 
is well described given the periodicity of the 3D crystal throughout the space.  
%since this volume is used to represent the crystal 
%periodically throughout the space.  
In the case of 2D materials, however, such repetition is artificial along the direction 
perpendicular to the plane. Despite of the simplicity of this argument,  
any calculation performed using such

@@

as a function of $L$ for P$\bar{6}$m2 transition metal

@@

respectively). Both components of the dielectric constant 
change systematically with $L$ without a clear convergence. 

@@

techniques, G$_{\rm 0}$W$_{0}$, invariably give alike
results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}). 
We have also undertaken similar analysis into the frequency regime 
for $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ where despite of the 
method utilized from PBE, G$_{\rm 0}$W$_{0}$ up 
to taking into account electron-hole excitations at the level of the 
Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$--BSE) the dependence on $L$
is still present (see Supplementary Section \ref{SI-ssec:gw} for a systematic study). 
These results indicate that quantities that depend 
on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, for instance, 
the optical absorption, suffer the
same deficiencies.  

@@

of the respective bulk materials (see Supplementary Section

@@

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq.~\ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Section \ref{SI-ssec:gw}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability,
comparison with other methods, simulations at the frequency-dependent domain
 can be found in Supplementary Section \ref{SI-ssec:gw}.

@@

\ref{SI-sec:pol-2D-Eg}). 
%It is worth mentioning that materials with
%elements having large polarizabilities, such as Hf and Zr in
%1T-HfO$_2$ or 1T-ZrO$_2$, respectively, also transfer alike features
%for the layers with slightly variations between 1T and 2H phases. The
%former normally shows larger values of
%$\alpha_{\mathrm{2D}}^{\parallel}$ than the latter.
%\todo[inline]{sorry but I don't quite get the idea of this
%  sentence. In fact HfO2 and ZrO2 have quite low in-plane
%  polarizabilities compared with even TiO2. Shall we just remove these
%  sentenses? }

@@

of theory are needed to predict bandgaps. See Supplementary Section \ref{SI-sec:gpaw}
for a benchmark of Eqs.~\ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using different bandgaps, databases, and levels of calculation.

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where $i$, $j$ are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom $i$ (Figure \ref{fig-3}{\bf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
\ref{fig-3}{\bf d}), which agrees well with Eq \ref{eq:2D-Moss-perp}.
This result indicates that $\alpha_{\mathrm{2D}}^{\perp}$ has a strong
physical meaning through the geometry of the layer.  Similar to the
molecular polarizability which characterizes the volume of the electron
cloud of an isolated molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the thickness of the 2D
material. Supplementary Section
\ref{SI-ssec:theory-1-perp-fundamental} shows an electrostatic model 
of this behavior. Indeed, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
\ref{fig-3}{\bf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, measurable via
electronic and optical approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
is in reality the (dielectric) characteristic thickness of a 2D
material, and can be used to resolve the long-existing controversy
about the experimental thickness of 2D materials, such as graphene
\cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06 level, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
database \cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\bf c} and
\ref{fig-3}{\bf d} (see details in Supplementary Section
\ref{SI-sec:gpaw-1}). Although the dielectric properties may be
overestimated at PBE level due to underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results (see
details in Supplementary Section \ref{SI-sec:gpaw-2}).

@@

We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
%The dielectric constant $\varepsilon$, although not well-defined for
%a monolayer 2D material, becomes applicable when the 2D layers are
%stacked. 
%
%
%
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\bf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis) as shown in Figure \ref{fig-4}{\bf b} and \ref{fig-4}{\bf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.
